When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-04-20 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
replaced protocol registration link
corrected BF10 papaja paste error

The Stage 1 Registered Report protocol has been approved and is available at [osf.io/qa2bg/](https://osf.io/qa2bg/).

@@

The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r paste(unlist(strsplit(apa_print(hypothesis3b_BF_levels)$statistic$level, split='} \\pm', fixed=TRUE))[1],"}$")`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r paste(unlist(strsplit(apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian, split='} \\pm', fixed=TRUE))[1],"}$")`).
Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median, so evidence was in favour of H3b.
Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (Figure\ \@ref(fig:h3b-plot)).

>>>>

The Stage 1 Registered Report protocol has been approved and is available at [osf.io/cpxth/](https://osf.io/cpxth).

@@

The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`).
Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median, so evidence was in favour of H3b.
Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (Figure\ \@ref(fig:h3b-plot)).

### 2023-04-20 06_Paper/COG-ED/Stage 2/Manuscript.tex
replaced protocol registration link
corrected BF10 papaja paste error

The Stage 1 Registered Report protocol has been approved and is available at \href{https://osf.io/qa2bg/}{osf.io/qa2bg/}.

@@

The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of \(n\)-back level (\(F(2.10, 239.56) = 154.50\), \(p < .001\), \(\hat{\eta}^2_G = .223\), 90\% CI \([.159, .282]\), \(\mathrm{BF}_{\textrm{10}} = 2.22 \times 10^{45}\) \}\$) and an interaction between \(n\)-back level and NFC scores (\(F(2.10, 239.56) = 4.93\), \(p = .007\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .025]\)), but no main effect of NFC scores (\(F(1, 114) = 3.22\), \(p = .075\), \(\hat{\eta}^2_G = .022\), 90\% CI \([.000, .084]\), \(\mathrm{BF}_{\textrm{10}} = 1.75 \times 10^{2}\) \}\(). Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (\)t(114) = -2.15\$, \(p = .033\), \(\mathrm{BF}_{\textrm{10}} = 11.15\)) and for 4-back (\(t(114) = -2.89\), \(p = .005\), \(\mathrm{BF}_{\textrm{10}} = 336.88\)) than those with NFC scores above the median, so evidence was in favour of H3b.
Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of \(n\)-back levels (Figure~\ref{fig:h3b-plot}).

>>>>

The Stage 1 Registered Report protocol has been approved and is available at \href{https://osf.io/cpxth}{osf.io/cpxth/}.

@@

The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of \(n\)-back level (\(F(2.10, 239.56) = 154.50\), \(p < .001\), \(\hat{\eta}^2_G = .223\), 90\% CI \([.159, .282]\), \(\mathrm{BF}_{\textrm{10}} = 2.22 \times 10^{45}\)) and an interaction between \(n\)-back level and NFC scores (\(F(2.10, 239.56) = 4.93\), \(p = .007\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .025]\)), but no main effect of NFC scores (\(F(1, 114) = 3.22\), \(p = .075\), \(\hat{\eta}^2_G = .022\), 90\% CI \([.000, .084]\), \(\mathrm{BF}_{\textrm{10}} = 1.75 \times 10^{2}\)).
Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (\(t(114) = -2.15\), \(p = .033\), \(\mathrm{BF}_{\textrm{10}} = 11.15\)) and for 4-back (\(t(114) = -2.89\), \(p = .005\), \(\mathrm{BF}_{\textrm{10}} = 336.88\)) than those with NFC scores above the median, so evidence was in favour of H3b.
Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of \(n\)-back levels (Figure~\ref{fig:h3b-plot}).
